Deep learning approaches on musical assisted-orchestration: an evaluation study

### 2020-05-04 paper/latex/paper.tex
Add quantitative evaluation

We performed experiments varying the number instruments used to form combinations, and varying the number of instruments used in each combination. (insert table of data showing the results of CNN with 2,3,4 etc instruments). An arbitrary number of samples can be used in the solution, since the $n$ highest probabilities can be taken from the output, leading to $n$ samples in the solution.

@@

\section{Evaluation and Conclusions}
- the approach seems promising for orchestration
- many things used in Orchidea are not implemented here (symbolic constraints, sparsity,...)
- CNN seems better for timbre
- ResNet seems better for pitch (what are timbre and pitch??)

@@

>>>>

Our final model was trained on data where each input was a combination of ten instruments, but we performed experiments with varying numbers of instruments used in combination. (insert table of data showing the results of CNN with 2,3,4 etc instruments) An arbitrary number of samples can be used in the solution, since the $n$ highest probabilities can be taken from the output, leading to $n$ samples in the solution.

@@

For quantitative evaluation, we orchestrated the same targets with OrchIdea, then compared the distance between our solutions and the targets and OrchIdea's solutions and the targets. The distance metric we used was 
$$d(x^t, \tilde{x}^t) =\lambda_1 \sum_k \delta_k^t(x_k^t - \tilde{x	}_k^t) + \sum_k \delta_k^t|x_k^t - \tilde{x	}_k^t|$$
$$\delta_k^t = 
\begin{cases}
1, \text{if} (x_k - \tilde{x}_k) < 0 \\
0, \text{otherwise}
\end{cases} $$
\section{Evaluation and Conclusions}
- the approach seems promising for orchestration
- many things used in Orchidea are not implemented here (symbolic constraints, sparsity,...)
- CNN seems better for timbre
- ResNet seems better for pitch (what are timbre and pitch??)

@@

Future steps in this project include implementing various methods that are present in OrchIdea.

Our current model orchestrates all targets using the same number of samples, and this does not take into account the density of different targets. The solution to this is to allow sparse solutions in which the model decides how many samples should be used to best represent the target. This allows a small number of samples to be used for sonically sparse sounds and many to be used for sonically dense sounds.

Partial filtering is a method that would aid our model in orchestrating the harmonics of a target. The dominant harmonic partials of the target are identified, and the search space is limited to only include samples of those pitches. For example, if the target is a recording of an instrument playing a C4, then the partials identified may be C4, C5, G5, and E6. The model would then only consider samples of these pitches to be used in the solution. This leads to a solution whose harmonics are much closer to the target, which is an important part of aural similarity.
